---
title: "ramblings"
author: "Matthew Wile"
date: "2024-04-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

General Goal : Communication

In an enterprise situation, how important is it to first be necessary and second to ensure others know you're necessary.

The point of this app then is as a communication tool into the finance professionals process.

Ideas:
- Difference between commodity and producer equity. How related are they, why or why not in specific instances?
- Forward curves. What is this suggesting about the market? About the general economic state?
- Risk management techniques. How important is it to levy risk? What happens if you don't?
- Describe the role of the finance professional in the enterprise

Data Examples
A) Commodity-Producer Comparisons
1. Palladium & Platinum vs Sibanye-Stillwater @SBSW
2. Silver vs Pan-American Silver @PAAS
3. Gold vs Barrick Gold @GOLD
--> Understanding the commodity, what makes it different? What else is SBSW exposed to?
B) Forward curves of gold and silver
--> What is this suggesting about these markets? About the economic state? How do they differ? How are they similar? 



```{r}
library(worldfootballR)
brasil <- worldfootballR::fb_teams_urls("https://fbref.com/en/comps/24/Serie-A-Stats")
palmeiras <- worldfootballR::fb_player_urls(brasil[13])
scout <- data.frame()
for (i in 1:length(palmeiras)) {
  s <- worldfootballR::fb_player_season_stats(player_url = palmeiras[i], stat_type = "standard")
  scout <- rbind(scout, s)
}

p <- brasil[13]
ts <- fb_squad_wages(team_urls = p)
```

